### 2020-01-11 work.Rmd
getting functions written is good!

```{r}
pars_1_dif <-
    read_csv("data-parameters/kopf2015-8.csv") %>%
    arrange(desc(easy)) %>%
    mutate(
        item = row_number(),
        nuisance_disc = c(0, 0, 0, 0.2, 0, 0, 0, 0)
    )

sim_1_dif <- sim_bias(pars = pars_1_dif, n_ref = 10000, n_foc = 10000, mean_foc = -1)

dif_constrained_baseline_one_at_a_time(data = sim_1_dif$data, groups = sim_1_dif$groups)
```

```{r}
pars_3_dif <-
    read_csv("data-parameters/kopf2015-8.csv") %>%
    arrange(desc(easy)) %>%
    mutate(
        item = row_number(),
        nuisance_disc = c(0, 0, 0, 0.5, 0.5, 0.5, 0, 0)
    )
```

>>>>

```{r}
pars_1_dif <-
    read_csv("data-parameters/kopf2015-8.csv") %>%
    arrange(desc(easy)) %>%
    mutate(
        item = row_number(),
        nuisance_disc = c(0, 0, 0, 0.1, 0.1, 0, 0, 0)
    )

sim_1_dif <- sim_bias(pars = pars_1_dif, n_ref = 50000, n_foc = 50000, mean_foc = -1)
```

```{r}
all_other <- dif_all_other(sim_1_dif$data, sim_1_dif$groups)

iterative_backward <- dif_iterative_backward(sim_1_dif$data, sim_1_dif$groups, all_other)
```
